### 2015-11-27 practice/post_thesis/monty_simple_pde_fwd/description.tex
add scaling to influx and source terms so that they have correct/more reasonable units

There is an influx $(\vec{v}c-nD\nabla c)\cdot\hat{n}=5\textrm{ ppb}$ at the west boundary. There is no flux through the north and south boundaries, and no flux through the top or bottom. The east boundary $\Gamma_e$ has a ``mass flow out'' boundary condition. There does not appear to be a consensus as to how to model a lack of a boundary in a transport equation; the simplest approach is the Danckwerts boundary condition $\frac{\partial c}{\partial n}=0$.

Given these boundary conditions and the alignment of the velocity, axes and boundaries, the weak form of the governing equation with test function $w$ is
\begin{multline*}
\int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c - nD\nabla c) - w\lambda nc + wf \dV \\
= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_\Gamma wn(D\nabla c)\cdot\hat{n} \dA\\
= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} c\vec{v}\cdot\hat{n}-5 \dA,
\end{multline*}
where $\Gamma_w$ is the west boundary.

>>>>

There is an influx $(\vec{v}c-nD\nabla c)\cdot\hat{n}=(5\textrm{ ppb})\vec{v}\cdot\hat{n}$ at the west boundary. There is no flux through the north and south boundaries, and no flux through the top or bottom. The east boundary $\Gamma_e$ has a ``mass flow out'' boundary condition. There does not appear to be a consensus as to how to model a lack of a boundary in a transport equation; the simplest approach is the Danckwerts boundary condition $\frac{\partial c}{\partial n}=0$.

Given these boundary conditions and the alignment of the velocity, axes and boundaries, the weak form of the governing equation with test function $w$ is
\begin{multline*}
\int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c - nD\nabla c) - w\lambda nc + wf \dV \\
= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_\Gamma wn(D\nabla c)\cdot\hat{n} \dA\\
= \int_\Omega w\frac{\partial c}{\partial t} - w\nabla\cdot(\vec{v}c) - \nabla w\cdot (nD\nabla c) - w\lambda nc + wf \dV + \int_{\Gamma_w} c\vec{v}\cdot\hat{n}+5 \dA,
\end{multline*}
where $\Gamma_w$ is the west boundary.
